\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2012-11-26 paper/mswp2012-proposal.tex

%Als Vorgehensmodell für dieses Projekt wurde das User Centered Design ausgewählt. Um ein effektives, interaktives System zu bauen müssen die Benutzer identifiziert und ihre Auf- gaben und Bedürfnisse studiert werden. User Centered Design ist ein iterativer Prozess, der dieses Vorhaben unterstützt und der im Wesentlichen folgende vier Phasen durchläuft[10]:
%1. Analyse des Nutzungskontextes
%2. Definition der Anforderungen
%3. Konzeption und Entwurf/Prototyping 4. Evaluation
%Im Rahmen dieser Arbeit sollen für das Projekt In-Kontakt die Phasen 1 bis 3 durchlaufen werden.

\subsection{User Centered Design}
We chose User Centered Design as the procedure model for the modern health care system.

\begin{figure}[tb]
	\centering
		\includegraphics[width=1\textwidth]{images/UCD.pdf}
	\caption{User Centered Design}
	\label{fig:images_UCD}
\end{figure}

>>>>

\subsection{User Centered Design}
We chose \emph{User Centered Design} as the procedure model used for the modern health care system. We need to identify and evaluate the users and their needs as a prerequisitory for building an effective and interactive system. User Centered Design is an iterative process that aims at supporting this procedure by integrating the user into the design process. By the means of user research and a systematic usability enginerring process it is possible to identify how user think and work. User Centered Design focuses on the solution and the quality of the user experience, in contrast to traditional methods to emphasize functionality and robustness of systems. User Centered Design runs through 4 phases [see figure \ref{fig:UCD}]:

\begin{enumerate}
	\item Research Phase
	\item Design Phase
	\item Prototyping Phase
	\item Evaluation Phase
\end{enumerate}

\begin{figure}[htb]
	\centering
		\includegraphics[width=1\textwidth]{images/UCD.pdf}
	\caption{User Centered Design}
	\label{fig:UCD}
\end{figure}
